Discriminative Sensing Based on Signal Processing

### 2017-10-17 docs/thesis/chapters/2_pca_svm_cfa/pca_svm_cfa.tex
minor improvements

\chapter{PCA and SVM for Critical Factors Analysis}
\label{ch:2_pca_svm_cfa}

@@

There is a significant continuous public spending on information technology (IT) by the Brazilian Federal Public Administration. In order to monitor and to diagnose the concerned public institutions IT governance (ITG), the Federal Court of Accounts, in Portuguese Tribunal de Contas da União (TCU), surveys data from these institutions practices as well as best practices for IT in government and business. These surveys started in 2007 with 39 questions and nowadays they contain more than 100 questions impacting on the ITG of Brazilian public institutions. Moreover, these questions encourage public institutions to adopt best practices not only in IT but also in all other management areas. In this paper, we propose the identification and the verification of the critical success factors (CSFs) of the TCU survey variables by means of statistical analysis. The CSFs are defined as the factors that most contributed for the high performance of the institutions and they are measured by using the ITG index created by TCU. Therefore, in order to validate our results, the statistically identified CSFs are compared with those mentioned by the public administration IT executives in interviews. Besides the statistical analysis, we successfully apply the Support Vector Classification (SVC) algorithm to classify public institutions in terms of their ITG index. By comparing the SVC based classification with the CSFs obtained from the interviews, we show that there is a very high level of similarity. Hence, the CSFs identified with SCV provide a very high impact, regarding the public administration ITG.

2.3 Análise de Componentes Principais

@@

2.4 Máquinas de Vetores de Suporte (MVS)

@@

2 Eliminação Recursiva de Variáveis (ERV)

@@

4.3 Análise das componentes principais

@@

4.4 Máquinas de Vetores de Suporte

>>>>

\chapter{Critical Success Factor Analysis Based on Feaure Selection}
\label{ch:2_pca_svm_cfa}

@@

Critical success factor (CSF) is a management term for an element that is necessary for an organization or project to achieve its mission. CSFs represent those managerial or enterprise areas that must be given special and continual attention to bring about high performance. CSF analysis is one challenger strategic management tool, but if properly applied, CSF analysis does provide a robust and very practical assessment for strategic planners.

The Tribunal de Contas da União (Federal Court of Accounts, often referred to as TCU) is the Brazilian federal accountability office that surveys data from public organizations in order to classify the maturity of IT governance.

Feature selection...

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) and recurive feature elimination (RFE) combined with Support Vector Machine (SVM), applied to the surveys data from public organizations, in order to identify the CSF for IT governance measured by TCU.

The resusts show that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn the classification adopted by TCU for IT governance evaluation. Therefore, SVM is used to highlight the more significant features for RFE, which corroborates with previous qualitative analysis for critical success factor identification.

\section{Related Works}
\label{sec:relatedworks}

...

\section{Data Model}
\label{sec:datamodel}

...

\section{Proposed Framework for Detection and Identification of Network Attacks}
\label{sec:prop_getv}

\subsection{Análise de Componentes Principais}

@@

\subsection{Máquinas de Vetores de Suporte}

@@

\subsection{Eliminação Recursiva de Variáveis (ERV)}

@@

\section{Experiments and Results}
\label{sec:experimentalresults}

\subsection{Análise das componentes principais}

@@

\subsection{Máquinas de Vetores de Suporte}
